Title

### 2023-06-22 main.tex
Programming the flux capacitor

\begin{flushleft}
{\Large
\textbf\newline{Title of submission to PLOS journals} % Please use "sentence case" for title and headings (capitalize only the first word in a title (or heading), the first word in a subtitle (or subheading), and any proper nouns).
}
\newline
% Insert author names, affiliations and corresponding author email (do not include titles, positions, or degrees).
\\
Tomás Basile\textsuperscript{1,2\Yinyang},
Carlos Pineda\textsuperscript{2*\Yinyang},
\\
\bigskip
\textbf{1} Facultad de Ciencias. Universidad Nacional Autónoma de México, Ciudad de México 01000, Mexico
\\
\textbf{2} Instituto de Física, Universidad Nacional Autónoma de México, Ciudad de México 01000, México
\\
\bigskip

@@

\end{flushleft}
% Please keep the abstract below 300 words
\section*{Abstract}
Pauli channels are fundamental in the context of quantum computing as they model noise in quantum devices. 
We propose a quantum algorithm for simulating Pauli channels on quantum computers 
and extend it to encompass Pauli dynamical maps 
(parametrized Pauli channels).
A parametrized quantum circuit is employed to accommodate for dynamical maps. 
We also establish the mathematical conditions for an
N-qubit transformation to be achievable using a parametrized circuit where
only one single-qubit operation depends on the parameter. 
The implementation of the proposed circuit is demonstrated using IBM's quantum computers 
for the case of one qubit, and the fidelity of this implementation is obtained.

% Please keep the Author Summary between 150 and 200 words
% Use first person. PLOS ONE authors please skip this step. 
% Author Summary not valid for PLOS ONE submissions.   
%\section*{Author summary}

@@

\cpnote{Porfa 3 propuestas de titulo y un intento de abstract. Ese es mas facil que la intro!
de neuvo, quizá vale la pena que te einspires en otros abstracts de PlosOne}
\tbnote{Va, ya puse un abstract basado en lo que vi en articulos de PlosOne}
\tbnote{Para el título, tengo las siguientes propuestas:}
{\color{green}
\begin{itemize}
\item Quantum Algorithm for Simulation of Parametrized Pauli Channels.
\item Parametrized Pauli Channels Simulation in Quantum Computes.
\item Quantum Simulation of Pauli Channels: Algorithm, Implementation and 
generalization to parametrized channels.
\end{itemize}
}

Puntos hechos en el artículo:
\begin{itemize}
\item Propuesta de algoritmo para canal es de Pauli de N qubits y su simulación en compus cuánticas
\item Condiciones para que un circuito parametrizado use una sola rotación parametrizada. En particular luego aplicadas al algoritmo para mapas dinámicos de Pauli.
\end{itemize}

@@

In this article, our first objective is to present a 
quantum algorithm capable of simulating Pauli channels on quantum computers, 
and we demonstrate its implementation using IBM's quantum computers. 
This algorithm is designed to simulate any Pauli channel on a system of $N$ qubits,
and works by utilizing $2N$ ancilla qubits.

Expanding beyond discrete Pauli channels,
we introduce the concept of Pauli dynamical maps, 
defined as a continuous parametrization of
$N$-qubit Pauli channels. 
We adapt the algorithm developed for Pauli channels 
to accommodate these dynamical maps by employing a 
parametrized quantum circuit. 
Furthermore, we contribute to the body of work related to parametrized quantum circuits by establishing theorem \ref{theorem2},
which outlines the types of transformations that 
can be done using a parametrized circuit with the condition that only one
 single-qubit operation in the circuit may depend on the parameter.
We explicitly find the mathematical conditions for these types of
transformations and conclude about which 
Pauli dynamical maps can be done with them. 
\cpnote{Me gustaron mucho estos dos ultimos parrafos. Croe que se puede ir mencionando las secciones
y poner la info del siguiente parrafo aca. Ahora, no lo pongas a lo bestia, sino realmente
integrando e hilando las ideas. Si hay preguntas, me dices que tos.}
\tbnote{Va, pongo una versión de estos dos últimos párrafos pero incluyendo lo de las secciones del siguiente aquí:}

@@

\tbnote{Y esto ya se va entonces}
{\color{red}
The paper is organized as follows: In section \ref{sec: Pauli Channels} 
we provide  the definition of quantum channels and focus specifically on Pauli channels for systems of
$N$ qubits. 
In section \ref{sec: Circuit for a Pauli Channel} we present  the proposed circuit 
for implementing a Pauli channel of $N$ qubits in a quantum computer. 
Furthermore, we simulate it on IBM’s computers for the special case of $N=1$
and obtain the fidelity of this implementation.  
Section \ref{sec: 1PR Circuits} shifts the focus to parametrized quantum circuits, 
aiming to generalize the circuit for Pauli channels to accommodate Pauli dynamical maps. 
We introduce theorem \ref{theorem2} to determine the operations that can be 
performed using a parametrized circuit 
with only one single-qubit operation dependent on the parameter.
Finally, in section \ref{sec: 1PR circuit for a Pauli map} 
we apply this theorem for the circuit of Pauli dynamical
maps and show a couple of maps that fulfill the theorem's conditions.}

@@

\cpnote{Evaluar si al final ponemos algo al respecto de este comentario}
\cpnote{Del circuito, parece ue las fases de las bs gammas no omportan mucho (o nada). 
Esa libertad la hemos considerado? De alguna manera colapsan curvas de las que
hemos visto?} \tbnote{Sí, es una libertad que se tiene y he considerado y significa que hay muchas elecciones de $b_{\gamma}$ para un mismo canal.
Es una de las varias cosas que complicaba determinar uno a uno qué canales se pueden hacer.}

@@

Finally, we choose a unitary matrix $V$ with the condition that its first
row is equal to $e^{i\theta} (|a|,|b|,|c|,0)$
with $\theta$ an arbitrary real number.
That way, we can define $|a\rangle = V |a'\rangle$, $|b\rangle = V |b'\rangle$, $|c\rangle = V |c'\rangle$
and since $V$ is unitary, these unprimed vectors will fulfill the conditions of \eref{eq:conditions-vecs}.
Furthermore, the form of the first row ensures that the dynamical map begins at the identity,
since it implies that when $s=0$, the 
state created in \eref{eq:vec}
is
$|a\rangle + |b\rangle + |c\rangle = e^{i \theta} |0\rangle$,
which  corresponds with applying the identity channel.

The choice of such a matrix $V$ can be done at random as follows:
After setting the first row,
construct three vectors $\vec{w}_1 , \vec{w}_2, \vec{w}_3$ orthogonal to it
using the Gram-Schmidt process.
Then select random complex numbers $r_1, r_2, r_3$ such
that $|r_1|^2 + |r_2|^2 + |r_3|^2 = 1$ and
define the second row of $V$ to be
$r_1 \vec{w}_1 + r_2 \vec{w}_2 + r_3 \vec{w}_3$.
Once the first two rows are chosen, use Gram-Schmidt to find two vectors
$\vec{v}_1, \vec{v}_2$ orthogonal to 
them and similarly define the third row as $q_1 \vec{v}_1+ q_2 \vec{v}_2$
with $|q_1|^2 + |q_2|^2$ and $q_1,q_2$
selected at random. 
Finally, there is only one choice for the fourth row so that it is 
orthonormal to the first three
and a random phase can be given to it.

>>>>

\begin{flushleft}
{\Large
\textbf\newline{Quantum simulation of Pauli channels and dynamical maps: algorithm and implementation } % Please use "sentence case" for title and headings (capitalize only the first word in a title (or heading), the first word in a subtitle (or subheading), and any proper nouns).
}
\newline
% Insert author names, affiliations and corresponding author email (do not include titles, positions, or degrees).
\\
Tomás Basile\textsuperscript{1,2\Yinyang},
Carlos Pineda\textsuperscript{2*\Yinyang},
\\
\bigskip
\textbf{1} Facultad de Ciencias. Universidad Nacional Autónoma de México, Ciudad de México 01000, Mexico
\\
\textbf{2} Instituto de Física, Universidad Nacional Autónoma de México, Ciudad de México 01000, México
\\
\bigskip

@@

\end{flushleft}
% Please keep the abstract below 300 words
\section*{Abstract}
\cpnote{Revisar}
Pauli channels are fundamental in the context of quantum computing as they
model noise in quantum devices.  We propose a quantum algorithm for simulating
Pauli channels on quantum computers 
and extend it to encompass Pauli dynamical maps 
(parametrized Pauli channels).
A parametrized quantum circuit is employed to accommodate for dynamical maps. 
We also establish the mathematical conditions for an
N-qubit transformation to be achievable using a parametrized circuit where
only one single-qubit operation depends on the parameter. 
The implementation of the proposed circuit is demonstrated using IBM's quantum computers 
for the case of one qubit, and the fidelity of this implementation is obtained. 
% Please keep the Author Summary between 150 and 200 words
% Use first person. PLOS ONE authors please skip this step. 
% Author Summary not valid for PLOS ONE submissions.   
%\section*{Author summary}

@@

@@

% In this article, our first objective is to present a 
% quantum algorithm capable of simulating Pauli channels on quantum computers, 
% and we demonstrate its implementation using IBM's quantum computers. 
% This algorithm is designed to simulate any Pauli channel on a system of $N$ qubits,
% and works by utilizing $2N$ ancilla qubits.
% 
% Expanding beyond discrete Pauli channels,
% we introduce the concept of Pauli dynamical maps, 
% defined as a continuous parametrization of
% $N$-qubit Pauli channels. 
% We adapt the algorithm developed for Pauli channels 
% to accommodate these dynamical maps by employing a 
% parametrized quantum circuit. 
% Furthermore, we contribute to the body of work related to parametrized quantum circuits by establishing theorem \ref{theorem2},
% which outlines the types of transformations that 
% can be done using a parametrized circuit with the condition that only one
%  single-qubit operation in the circuit may depend on the parameter.
% We explicitly find the mathematical conditions for these types of
% transformations and conclude about which 
% Pauli dynamical maps can be done with them. 
% \cpnote{Me gustaron mucho estos dos ultimos parrafos. Croe que se puede ir mencionando las secciones
% y poner la info del siguiente parrafo aca. Ahora, no lo pongas a lo bestia, sino realmente
% integrando e hilando las ideas. Si hay preguntas, me dices que tos.}
% \tbnote{Va, pongo una versión de estos dos últimos párrafos pero incluyendo lo de las secciones del siguiente aquí:}
%

@@

@@

% \cpnote{Evaluar si al final ponemos algo al respecto de este comentario}
% \cpnote{Del circuito, parece ue las fases de las bs gammas no omportan mucho (o nada). 
% Esa libertad la hemos considerado? De alguna manera colapsan curvas de las que
% hemos visto?} \tbnote{Sí, es una libertad que se tiene y he considerado y significa que hay muchas elecciones de $b_{\gamma}$ para un mismo canal.
% Es una de las varias cosas que complicaba determinar uno a uno qué canales se pueden hacer.}
%

@@

{\color{purple}
Finally, we choose a unitary matrix $V$ with the condition that its first
row is equal to $e^{i\theta} (|a|,|b|,|c|,0)$
with $\theta$ an arbitrary real number.
That way, we can define $|a\rangle = V |a'\rangle$, $|b\rangle = V |b'\rangle$, $|c\rangle = V |c'\rangle$
and since $V$ is unitary, these unprimed vectors will fulfill the conditions of \eref{eq:conditions-vecs}.
Furthermore, the form of the first row ensures that the dynamical map begins at the identity,
since it implies that when $s=0$, the 
state created in \eref{eq:vec}
is
$|a\rangle + |b\rangle + |c\rangle = e^{i \theta} |0\rangle$,
which  corresponds with applying the identity channel.

The choice of such a matrix $V$ can be done at random as follows:
After setting the first row,
construct three vectors $\vec{w}_1 , \vec{w}_2, \vec{w}_3$ orthogonal to it
using the Gram-Schmidt process.
Then select random complex numbers $r_1, r_2, r_3$ such
that $|r_1|^2 + |r_2|^2 + |r_3|^2 = 1$ and
define the second row of $V$ to be
$r_1 \vec{w}_1 + r_2 \vec{w}_2 + r_3 \vec{w}_3$.
Once the first two rows are chosen, use Gram-Schmidt to find two vectors
$\vec{v}_1, \vec{v}_2$ orthogonal to 
them and similarly define the third row as $q_1 \vec{v}_1+ q_2 \vec{v}_2$
with $|q_1|^2 + |q_2|^2$ and $q_1,q_2$
selected at random. 
Finally, there is only one choice for the fourth row so that it is 
orthonormal to the first three
and a random phase can be given to it.
}
